%
\documentclass[12pt]{letter} 
\usepackage{amsmath, amssymb, mathrsfs, amsfonts,  amsthm}
\signature{Yasha Savelyev}
%\location{1075 Evans}
%\telephone{(510)643-0893 (office), \,\,\,(510)883-9938 (home)}
%\email{yasha@math.sunysb.edu} 
\name{Yasha (Yakov) Savelyev}
\address{Bernal Díaz del Castillo 340, \\
Col. Villas San Sebastian,\\
28045 Colima, Colima, \\
Mexico \\
 } 
%\letterheadanyway
 \signature{Yasha Savelyev} 
 %\adjustmargins{.25in}
\date{Fall 2018}
\begin{document}

\begin{letter}{
}
\opening{Dear Application Committee:}   
I am applying for the assistant professor position. I am an independent researcher and enjoy teaching and dealing with students.
I also have much experience, having had a teaching postdoc at Umass Amherst, 
and non-teaching fellowships at CRM Montreal, and ICMAT Madrid. I also spent a semester as a postdoctoral fellow at MSRI, and a
month at Tel Aviv university and at the Research Institute for mathematical
sciences at Kyoto university as invited visitor. Currently I have a permanent contract at University of Colima,  Mexico, where I am teaching 1-2 courses a semester, (and recently exactly 2).
I received my PhD under the 
guidance of Dusa McDuff
in August 2008 from
the Department of Mathematics at SUNY Stony Brook.  
   
   While I am fairly happy at my current university,  
I have some misgivings, which I suppose I should share.
First isolation, I would like to work with more students, to give an example there are only two currently in their junior year, although they are rather good. 
I would also like to advise some PhD students, I have many ideas to share. And of course I would like more fellow mathematicians to talk to, and in more diverse areas. For example I am learning a bit about distributed computing systems, and I have no one to talk to about that here. I am working on some problems in dynamics, in which I have no formal training, and it would be super to have an expert to talk to, etc.
Another issue is difficulty in Mexico in obtaining a good grant for research, there are simply too many good applications for the funding available.
Finally, in the last few years there was a very disturbing spike in cartel violence in the state of Colima, and it is now the most dangerous state in Mexico per capita. 


I think I would be very happy at the University of Illinois at Chicago.  It is a very diverse department, 
which suits my rather diverse interests,  and the location of the university
is highly appealing. 



% Michigan state looks like a super exciting place to do mathematics and
% in particular geometry-topology. I would be happy to interact with
% Casim Abbas and Matthew Hedden with whom I share my immediate interests in symplectic
% geometry, as well as Xiaodong Wang and other members of the
% department. The location of the university is appealing to me and I
% really look forward to returning to the USA.
% % The tenure track position at Queens college is highly interesting to me
% % for a number of reasons. Some of the recent  developments in my research
% % intersect aspects of algebra and algebraic geometry, and so could lead
% % to some discussions  with Scott Wilson and John Terilla among others. 
% % I would also have access to all the other great
% % universities in NYC which needless to say would be fantastic for
% % developing my ideas.

% Besides that NYC is a
% fantastic place to teach mathematics and do research. I went to
% the nearby John Bowne high school, straight after emigrating from
% Moscow, Russia and grew to love the student
% diversity of New York. No culture shock for me, it was just a fantastic
% experience, and frankly a refreshing break from the rather elitist, at
% the time, atmosphere in education in Moscow.
% My AP calculus teacher Arthur Samel, with whom I am still in touch, certainly
% played a big role in my choice to pursue study of higher mathematics,
% and I would like to think I could similarly help inspire some students.
%
% On a (even) more personal note my immediate family is currently based in NYC,
% with my sister just starting college,
% and this makes this position even more attractive.

My research interests are in the areas of symplectic and differential geometry, 
with keen interest in exploring connections with algebraic topology and dynamics,  with a
good percentage of my recent work along these lines.  In particular I recently
establish some  relationships between the theory of Fukaya $A _{\infty} $
categories, Hamiltonian fibrations in symplectic geometry and abstract
algebraic topology, particularly the theory of quasi-categories of Joyal,
especially after work of Lurie. This project may be summarized as trying to categorify Novikov-Pontryagin theory using Floer homology techniques.
In a different and much more basic direction, I am researching new rigidity phenomena in locally conformally symplectic geometry, 
and the dynamical phenomenon of sky catastrophes for Reeb vector fields. I have also been interested in computer science.
% But most exciting is the construction of
% ``Euler'' classes, associated to Hamiltonian fibrations, in a certain generalized cohomology theory coming from the
% space of $A _{\infty} $ categories (constructed recently in my work). In the
% future this
% would allow application of powerful methods of abstract algebraic topology
% (like the Mayer-Vietoris sequence) to
% computation of certain Gromov-Witten invariants, or more specifically quantum
% characteristic classes originally defined in my thesis.
% I also have done some work in Hofer geometry  of the group of Hamiltonian diffeomorphisms of a 
% symplectic manifold, which is a highly interesting and natural
% bi-invariant Finsler geometry on this group. This geometry gives rise to a vast
% number of extremely difficult questions, with very elementary formulation,
% which makes it a very attractive object of study. One of my principal
% contributions in this field
% is the development of ``Morse theory''
% for the Hofer length functional. This had a number of applications, and is also
% recently used for certain computations with the Fukaya
% category. 
% I have extensive teaching experience, I referee for mathematical journals, and for Zentralblatt.  
% I have given many seminar talks and a
% number of conference talks. 

 If
you have any further questions, please send email to 
{\sf yasha.savelyev@gmail.com} or call me at 413-570-0163. 
Thank you for your time and consideration.


\closing{Sincerely,} 


\end{letter}

\end{document} 
